%-------------------------
% Resume in Latex
% Original uthor credits : Aras Gungore
% Adapted by : Leo Guédez
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{amssymb}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

%---------- --> #comment #4974a5 > new custom item; ignore if needed. ----------

\newcommand{\fullcite}[1]{\item\parbox[t]{\linewidth}{\fullcite{#1}}}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%---------- APA TEST FOR PUBLICATIONS SECTION ----------
\usepackage[style=apa, backend=biber, apamaxprtauth=99]{biblatex}
\DeclareLanguageMapping{english}{american-apa}
\addbibresource{references.bib}

\usepackage{hanging}

%---------- --> #comment #4974a5 > custom margin options ----------
%% \usepackage[left=2cm, right=2cm, top=2cm, bottom=2cm]{geometry}
%---------- --> #comment #4974a5 > custom margin options ----------

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\LARGE \scshape Leonardo Guédez} \\ \vspace{6pt}
    \small
    %% \faMobile \hspace{.5pt} \href{tel:192831045711}{+1 928 310 5711}
    %% $|$
    %% \faEnvelope \hspace{.5pt} \href{mailto:guedezle@msu.edu}{guedezle@msu.edu}
    %% $|$
    %% \faLinkedinSquare \hspace{.5pt}
    \href{https://www.linkedin.com/in/eleguedez/}{https://www.linkedin.com/in/eleguedez/}
    %% $|$
    %% $ \mathbb{X} $ \hspace{.5pt}\href{https://twitter.com/eleguedez}{Twitter}
    $|$
    \href{https://www.leonardo-guedez.com}{https://www.leonardo-guedez.com}
    %% $|$
    %% \faMapMarker \hspace{.5pt} \href{}{Michigan, USA}
\end{center}



%----------- EDUCATION -----------

\section{Education}
\vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Michigan State University
      % \normalfont{(Admission rate: 0.09\%)}
      }{East Lansing, MI, USA}
      {Ph.D. in Second Language Studies (SLS)} {May 2025 (Expected)}
      \vspace{3pt}

    \resumeSubheading
      {Northern Arizona University (as Fulbright scholar)
      % \normalfont{(Admission rate: 0.85\%)}
      }{Flagstaff, AZ, USA}
      {\small M.A. in Teaching English as a Second Language (TESL)} {2020}
      {\\ \vspace{6pt} \small \textit{(Applied Linguistics track, with distinction)}}
      \vspace{3pt}

    \resumeSubheading
      {Universidad Simón Bolívar
      % \normalfont{(Admission rate: 0.85\%)}
      }{Caracas, Venezuela}
      {M.A. in Applied Linguistics} {2017}
      \vspace{3pt}

    \resumeSubheading
      {Universidad Pedagógica Experimental Libertador
      % \normalfont{(Admission rate: 0.85\%)}
      }{Maracay, Venezuela}
      {B.A. in English Language Teaching (Magna Cum Laude)} {2013}

  \resumeSubHeadingListEnd



%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
\vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Michigan State University}{East Lansing, Michigan, USA}
      {Research Associate}{Jan 2023 \textbf{--} Present}

        \resumeItemListStart

          \resumeItem{Currently coding and cleaning interview data to examine the perceptions and attitudes of conversation partners regarding interaction training. A manuscript is being prepared to be submitted to a journal specializing in computer-assisted language learning.}
          \vspace{3pt}

          \resumeItem{Conducted interviews to conversation partners and stakeholders regarding the role of training in the teaching and learning of a second language in the context of synchronous video computer-mediated communication (SVCMC).}
          \vspace{3pt}

        \resumeItemListEnd

    \resumeSubheading
      {Michigan State University}{East Lansing, Michigan, USA}
      {Research Associate}{Jun 2022 \textbf{--} Present}

        \resumeItemListStart

          \resumeItem{Implemented mixed-effects logistic regression to analyze the dative alternation phenomenon in the context of second language acquisition. I personally annotated over nine predictors, carried out all statistical modeling in \textit{R}, and leveraged  corpus techniques such as tagging, concordancing, and applying regular expressions for data extraction and filtering.}
          \vspace{3pt}

          \resumeItem{Composed a detailed manuscript in \textit{Quarto} to present the results of the dative project, employing contemporary tools in data management such as \textit{Git}, \textit{Emacs}, and \textit{Vim} motions. This document is in line for submission to a prestigious journal specializing in corpus linguistics.}
          \vspace{3pt}

          \resumeItem{Performed Monte Carlo simulations on the dative alternation data, implementing model diagnostics on the binary response as influenced by the model predictors using \texttt{brms}. Additionally, conducted Principal Component Analysis and \texttt{anova} for dimensionality reduction and model comparison, respectively.}
          \vspace{3pt}

        \resumeItemListEnd
    
    \resumeSubheading
      {Michigan State University}{East Lansing, Michigan, USA}
      {Project Research Assistant}{Aug 2021 \textbf{--} May 2022}

        \resumeItemListStart

          \resumeItem{Developed and managed the Multilingual Repository of Applied Linguistics (MuRAL), a comprehensive digital collection of multilingual research abstracts. This involved extensive data compilation, categorization, and digital repository management.}
          \vspace{3pt}

          \resumeItem{Led a collaborative effort to expand the repository, successfully recruiting and overseeing a team of contributors for translating and integrating abstracts into MuRAL. Worked under the guidance and supervision of Dr. Meagan Driver, ensuring high standards of linguistic accuracy and academic relevance.}
          \vspace{3pt}

          \resumeItem{Utilized advanced data management techniques and software, enhancing the accessibility and utility of the repository for researchers and students in Applied Linguistics worldwide. Engaged in regular reviews and updates of the repository content to ensure its ongoing relevance and comprehensiveness.}
          \vspace{3pt}

        \resumeItemListEnd

\newpage
        
    \resumeSubheading
      {Michigan State University}{East Lansing, Michigan, USA}
      {Project Research Assistant}{Oct 2020 \textbf{--} July 2021}

        \resumeItemListStart

          \resumeItem{Completed specialized training in corpus linguistics, gaining proficiency in advanced linguistic analysis methods and tools. This included an in-depth study of corpus design, data annotation, and statistical analysis techniques, enriching my expertise in the field.}
          \vspace{3pt}

          \resumeItem{Authored a comprehensive literature review for a corpus-based research paper. This involved a critical analysis of existing literature, identifying key trends, gaps, and insights in corpus linguistics. The review laid the groundwork for subsequent research and was commended for its thoroughness and analytical depth.}
          \vspace{3pt}

          \resumeItem{Engaged in collaborative research activities, contributing to the development of innovative approaches in linguistic analysis. This role involved interacting with academic peers, participating in discussions, and applying new knowledge to ongoing research projects.}
          \vspace{3pt}

        \resumeItemListEnd
        
    \resumeSubheading
      {Michigan State University}{East Lansing, Michigan, USA}
      {Project Research Assistant}{Jun 2020 \textbf{--} Oct 2020}

        \resumeItemListStart

          \resumeItem{Engaged in a pivotal role in the TalkAbroad research project by meticulously transcribing interviews. This task was fundamental for the analysis and interpretation of qualitative data, contributing significantly to a publication in the field.}
          \vspace{3pt}

          \resumeItem{Played a key role in ensuring the accuracy and reliability of the transcribed data, which formed the basis for in-depth analysis and subsequent findings. My attention to detail and commitment to maintaining the integrity of the data were crucial in this process.}
          \vspace{3pt}

          \resumeItem{Collaborated closely with the research team to align the transcription work with the project's objectives. This collaboration ensured that the transcribed interviews effectively supported the broader research goals and facilitated meaningful insights into the study's focus area.}
          \vspace{3pt}
          
        \resumeItemListEnd

    \resumeSubheading
      {Northern Arizona University}{Flagstaff, AZ, USA}
      {Project Research Assistant}{Jan 2020 \textbf{--} Jun 2020}

        \resumeItemListStart

          \resumeItem{Participated in detailed speech analyses, focusing on language proficiency data within a research project. This involved the meticulous transcription of spoken language samples, ensuring accuracy and consistency in data capture.}
          \vspace{3pt}

          \resumeItem{Conducted extensive fluency analyses, applying rigorous methodologies to evaluate and interpret speech patterns. This process was instrumental in identifying key characteristics of language proficiency and fluency.}
          \vspace{3pt}

          \resumeItem{Reported on findings derived from various speech metric analyses. This involved synthesizing complex data into coherent and insightful reports, contributing to the broader understanding of speech dynamics in language proficiency.}
          \vspace{3pt}

          \resumeItem{Worked collaboratively with a team of researchers, contributing to the overall success of the project through diligent data analysis and effective communication of results.}
          \vspace{3pt}

        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- WORK EXPERIENCE -----------

\section{Teaching Experience}
\vspace{3pt}

  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Michigan State University}{East Lansing, Michigan, USA}
      {Spanish instructor}{Aug 2022 \textbf{--} Present}

        \resumeItemListStart

          \resumeItem{Actively instruct college students in Spanish as a foreign language, employing a comprehensive and adaptable teaching approach. This involves the meticulous preparation and customization of teaching materials to enhance the learning experience and cater to diverse student needs.}
          \vspace{3pt}

          \resumeItem{Implement a communicative approach to language teaching, focusing on practical and interactive learning. This method emphasizes student engagement and active participation, facilitating a more natural and effective acquisition of the Spanish language.}
          \vspace{3pt}

          \resumeItem{Provide targeted feedback and guidance to students, addressing their specific errors and challenges. My dedication to understanding and responding to individual learning styles and difficulties has been instrumental in improving their language proficiency and confidence in using Spanish in real-world scenarios.}
          \vspace{3pt}

          \resumeItem{Collaborate with academic peers to continually refine teaching methods and materials. This collaboration ensures that the course content remains relevant, engaging, and in line with current educational standards and practices.}
          \vspace{3pt}

        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards}
\vspace{2pt}

  \resumeSubHeadingListStart

    \small{\item{

      \textbf{College of Arts and Letters Summer Support Fellowship (2023):}{ A \$4,500.00 fellowship dedicated to the revision, approval, and journal submission of my qualifying research paper.}

      %% \textbf{College of Arts and Letters Summer Support Fellowship (2022):}{ A \$4,500.00 fellowship dedicated to the analysis and submission of my first qualifying research paper in the SLS Program.}

      %% \textbf{College of Arts and Letters Summer Support Fellowship (2021):}{ A \$4,500.00 fellowship granted to work on my first qualifying research paper, which fulfills a requirement leading towards graduation from the Ph.D. in MSU’s SLS Program.}

      \textbf{Fulbright Foreign Student Scholarship:}{ Two-year fully funded Fulbright scholarship for an M.A. in TESL at Northern Arizona University.}

    }}

  \resumeSubHeadingListEnd



%----------- PUBLICATIONS -----------

%% \section{Publications}
    %% {\fullcitebib{tracy2018can}}


%----------- SKILLS -----------

\section{Skills}
\vspace{2pt}

  \resumeSubHeadingListStart

    \small{\item{

      \textbf{Languages:}{ R/RStudio, Python, Bash, SQL}

      \textbf{Software \& Analytical Techniques:}{ Git, Quarto, Emacs, Vim, Natural Language Processing, Mixed-Effects Logistic Regression, Multivariate Statistical Modeling}

      \textbf{Spoken Languages:}{ Spanish (Native), English (Academic/Advanced)}
        
    }}

  \resumeSubHeadingListEnd



%----------- RELEVANT COURSEWORK -----------

\section{Relevant Coursework}
\vspace{2pt}

  \resumeSubHeadingListStart

    \small{\item{

\textbf{}{Advanced Statistics for Computational Linguistics I-II, Applied Machine Learning, High-Performance Computing and Terminal scripting, Computational Linguistics, Quantitative Research Methods, Qualitative Analysis in Ethnographic Research, Psycholinguistics I-II, Meta-analytic Methods in Applied Linguistics, Applied Educational Technology}
    }}

  \resumeSubHeadingListEnd



%----------- CERTIFICATES -----------

% \section{Certificates}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
  % \resumeSubHeadingListEnd



%----------- ORGANIZATIONS -----------

% \section{Organizations}
  % \resumeSubHeadingListStart
    
    % \resumeOrganizationHeading
      % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
  % \resumeSubHeadingListEnd



%----------- HOBBIES -----------

% \section{Hobbies}
  % \resumeSubHeadingListStart
    % \small{\item{Swimming, Fitness, Eight-ball}}
  % \resumeSubHeadingListEnd



%----------- REFERENCES -----------

% \section{References}
  % \resumeSubHeadingListStart
    
  % \resumeSubHeadingListEnd



%-------------------------------------------
\end{document}
